\section{Benchmark Construction}
\label{sec:benchmark-construction}

\paragraph{Unit of construction.}
HandoffBench targets state transfer at a fixed control boundary rather than
routing quality. Each episode fixes an authenticated upstream trace, source and
receiver roles, the boundary cut, a public action contract, deterministic mock
tools and user replies, and a machine-executable terminal predicate. The
evaluator-side boundary state is a set of typed atomic claims with exact trace
provenance and epistemic status (known, unknown, contradicted, or not applicable).
We include a claim only when changing or removing it can alter a legal next action
or terminal success. Goals, user constraints, verified business facts, ordinary
unresolved slots, scoped consent, and organizational policy checks are mutually
exclusive roles. Executable action preconditions remain in the public contract,
and tool-execution metadata remains in the trace; neither is duplicated as a
semantic claim for primary state F1.

\paragraph{Candidate-pool generation.}
We first authored a workflow blueprint---roles, causal trace, authority boundary,
plausible alternatives, legal sequence, and first user-impacting action---then
instantiated concrete synthetic dates, monetary values, statuses, scopes, option
attributes, and opaque identifiers with deterministic generators. Families are
the split unit: entity replacement or paraphrase does not create a new family.
The resulting \emph{candidate} pool has 200 unique families, evenly divided among
travel, commerce, procurement, enterprise IT, and scheduling (Table~\ref{tab:candidate-stats}).
Six preregistered stressors vary what must cross the boundary: long distractors,
conflicting evidence, irreversible actions, multi-step evidence, missing
authority, and user revisions. Of the 200 gold-path proposals, 195 contain a
user-impacting action.

Construction checks are deterministic and should not be confused with model
results. Schema, provenance, unique-key, argument-grounding, enum-permutation,
and action-sequence mutation tests pass, and the authored sequence executes in
200/200 simulators; an exact-copy oracle likewise reaches 200/200. These numbers
establish internal executability only, not task validity or agent competence.
When the hidden terminal predicate is withheld, only 137/200 public contracts
admit a unique legal terminal sequence; clarification or authority actions can
commute in 63. Moreover, only 305/990 proposed claims have a direct syntactic
counterfactual witness in a guard key or exact action argument. The remainder
may be semantically necessary, but static code cannot establish their minimal
causal relevance. Both sets therefore require independent human reconstruction.
Simple leakage diagnostics obtain 14/200 from the public catalog alone and 12/200
from predicate-only features. A stronger diagnostic is sometimes mislabeled
``name only'': it receives the oracle action-name sequence, then guesses the
first value in every public enum. It succeeds on 69/200 (34.5\%; Wilson 95\% CI
[28.3, 41.3]), versus 13.9\% expected under uniform enum guessing. All successes
occur when every correct enum value is first. This reveals combined oracle-name
and interface-ordering leakage, not that action names alone solve 34.5\%.

\begin{table}[t]
\centering
\small
\caption{Repository-static statistics for candidate v2. ``Oracle'' denotes
deterministic simulator consistency; human validation is pending.}
\label{tab:candidate-stats}
\begin{tabular}{@{}lr@{}}
\toprule
Statistic & Count / rate \\
\midrule
Candidate families (five domains) & 200 (40 each) \\
Primary stressors: LD / CE / IA & 38 / 35 / 35 \\
Primary stressors: ME / MA / UR & 32 / 30 / 30 \\
Proposed atomic claims & 990 \\
User-impacting gold paths & 195 / 200 \\
Static sequence / copy-oracle success & 200 / 200 \\
Unique legal sequence without predicate & 137 / 200 \\
Claims with direct syntactic witness & 305 / 990 \\
Catalog-only / predicate-only success & 7.0\% / 6.0\% \\
Oracle names + enum-first success & 69 / 200 (34.5\%) \\
Exact trace / action-graph collisions & 0 / 0 \\
Normalized topology overlaps & 69 candidates \\
Lexical pairs at Jaccard $\geq .80$ & 0 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Development-overlap audit.}
We compared the 200 candidates with 54 development episodes after normalizing
dates, numeric and opaque identifiers, and task/trace/boundary IDs. There are no
collisions in family ID, entity pool, generator seed, exact trace hash, normalized
trace hash, or exact action-graph hash, and no trace-content bigram pair reaches
the preregistered Jaccard threshold of .80. However, 69 candidate tasks share a
\emph{normalized} action-graph hash with at least one development task (552
candidate--development pair groups). This is distinct from the numerically equal
69 oracle-name/enum-first successes: the former diagnoses topology reuse across
splits, whereas the latter diagnoses public-interface ordering leakage within candidates.
Normalization may over-collapse common schema structure, but it may also reveal
genuine workflow similarity. We therefore do not describe the pool as
structurally held out or frozen; these cases require human review and
rejection/redesign before sealing.

\section{Planned Human Validation}
\label{sec:human-validation}

Human validation has not yet been executed, so we report no agreement statistic
and call no candidate a test item. The preregistered procedure assigns every
label-free packet to two annotators in independently randomized order. Annotators
see the authenticated trace, boundary roles, public actions, and deterministic
tool semantics, but not source labels, evaluator predicates, model outputs,
development results, family blueprints, or one another's responses. Each first
derives the exact legal action sequence, then independently reconstructs the
minimal claims, typed values and statuses, criticality, and one or more exact
\texttt{(trace\_id, source\_type, field\_path)} pointers. They also flag whether
irreversible arguments are inferable and whether catalog order or action names
leak the sequence.

Responses are schema-checked, hashed, and locked before comparison; corrections
create a new retained version rather than overwriting the original. We will
report one-to-one claim precision/recall/F1, exact typed-value and provenance
agreement, category/status/criticality agreement, and exact sequence agreement,
clustered by family. Cohen's $\kappa$ is used only when both annotators employ at
least two labels, with raw agreement and denominators always shown. A third
annotator receives disagreements only and may reject an ambiguous task. Tasks
with secret arguments, non-unique legal sequences, unresolved safety claims,
interface-ordering leakage that trivializes the decision, or problematic normalized
topology overlap must be rejected or regenerated before any confirmatory model
call. Only after adjudication, overlap remediation, final hashes, and a
non-overwritable manifest may a later version be called frozen.
