\section{Ethics and Limitations}
\label{sec:ethics-limitations}

All scenarios, entities, traces, policies, and tool outputs are project-authored
synthetic data, not customer records or private company policies; no real person
is intentionally represented. Benchmark annotation used two isolated LLM-agent
roles plus a disagreement-only adjudication agent, not recruited human
annotators. Their packets, locked responses, and hashes are retained, but the
exact underlying annotation-model/runtime identity was not recorded; agreement
therefore measures replicated agent judgments rather than human validity. An
independent human audit remains necessary before claiming human-grounded gold
labels. Generative-AI systems also assisted code generation, literature triage,
experiment orchestration, manuscript drafting, and internal review. The human
authors remain responsible for all submitted material; agent-produced citations
and claims require author verification before submission. Future free-text
annotations could introduce personal information, so exports require PII/secret
review. The tasks
simulate consequential purchases, refunds, identity and access checks,
accessibility requests, and travel-document workflows. Their simplified policies
are unsuitable for operational, legal, medical, financial, employment, or other
decisions about real people.

The sealed split is synthetic and may contain lexical regularities, simplified
jurisdictional assumptions, and limited real-world coverage. Its five authored
domains, deterministic user/tool simulators, and single handoff per episode do
not reproduce naturally occurring organizational communication, routing errors,
long-horizon memory, or emergent multi-party coordination. Isolated agent
reconstruction and deterministic checks establish procedural consistency, not
human or ecological validity.
The 30.5\% oracle-sequence-plus-enum-first diagnostic reveals ordered-enum
regularity under an evaluator-provided workflow path; it is not name-only
performance. Moreover, 69 normalized-topology overlaps with development tasks
preclude a claim of complete structural holdout, although there are no exact
development identity, trace, or action-graph collisions. A
post-seal replication can adapt separately licensed ToolSandbox scenarios and
the telecom subset of $\tau^2$-Bench \citep{lu2025toolsandbox,barres2025tau2},
but must report each source separately and may not replace rejected primary
families after outcomes are observed.
The confirmatory study is limited to two local 14B open-weight instruction
models, two seeds, synthetic single-handoff tasks, and deterministic mock tools;
it does not establish behavior in long-running collaboration or real
organizations. The Gold Oracle is an identifying intervention, not a deployable
baseline. The pooled checks result averages eight representation cells and does
not imply that enforcement, every validator, model, or domain benefits. Typing,
provenance, secondary endpoints, and subgroup intervals were outside the
confirmatory multiplicity family. The retained Ministral and replacement Qwen
arms were executed at different times, so an unmeasured environment batch
effect remains possible despite fixed snapshots, configuration, and data. A
post-run hardware/package snapshot is available for the replacement Qwen arm,
but no equivalent package-version snapshot was captured for the retained
Ministral arm. We
disclose the external service termination that invalidated the earlier Qwen arm;
the decision used infrastructure logs rather than scientific outcomes, and all
4,400 earlier Qwen rows were excluded.

Project-authored code is released under Apache-2.0 and project-authored
synthetic data under CC BY 4.0; the manuscript, author kit, model weights, and
third-party materials are excluded from those grants. The sealed tasks cannot
be repaired or filtered after model outcomes are observed, and the reported
confirmatory effects are not representativeness claims.
