% Development numbers are diagnostic only.
\section{Closest Related Work}

Learned communication studies optimize messages for cooperative tasks
\citep{sukhbaatar2016commnet,foerster2016dial}, while stateful tool-use and
collaboration benchmarks measure policy compliance, terminal success, and
team-level coordination
\citep{yao2024taubench,lu2025toolsandbox,zhu2025multiagentbench}. These lines do
not expose a scored semantic state at a fixed, manipulated role boundary. The
broad idea of evaluating agent handoffs is also not new. Most directly,
\emph{Handoff Debt} interrupts coding agents at deterministic repository
checkpoints and compares repository-only, raw-trace, summary-note, and
structured-note views, measuring task resolution and successor rediscovery
cost~\citep{kc2026handoff}. We therefore do not claim the first handoff
benchmark, controlled takeover, or structured transfer artifact. Our estimand
is instead the fidelity of a semantic interface at an inter-role boundary: each
episode exposes an evaluator-only set of atomic claims with epistemic status and
trace evidence, and tests which claim errors precede policy-invalid or
regressive actions. This also differs from state-probe and runtime-guard work
\citep{jia2026neurostate,she2026provenanceguard}
(Table~\ref{tab:closest-collisions}).
Concurrent work makes the collision sharper. PACT treats inter-agent messages
as compact public action-state updates and evaluates accuracy--cost trade-offs
\citep{huang2026pact}; AgentAsk annotates edge-level data gaps, referential
drift, signal corruption, and capability gaps, then learns when to clarify
\citep{lin2026agentask}; and EntCollabBench objectively scores role-specialized,
permission-isolated enterprise workflows in which context transfer is one
bottleneck \citep{yu2026entcollab}. HandoffBench does not claim these messaging,
repair, or enterprise settings. It contributes evaluator-visible atomic boundary
state and matched representation interventions that estimate oracle-gated
boundary regression and test serialization mechanisms under fixed evidence.

\begin{table}[t]
\centering
\small
\begin{tabular}{p{0.20\columnwidth}p{0.21\columnwidth}p{0.43\columnwidth}}
\toprule
Work & Primary object & Distinction of HandoffBench \\
\midrule
Handoff Debt
& Coding takeover and rediscovery under four context views
& Gold field-level boundary state; epistemic and authority-bearing claims;
oracle-gated transfer regression rather than repository resumability. \\
NeuroState-Bench
& Commitment integrity through side-query probes within an agent profile
& A manipulated predecessor--successor boundary and alternative transport
representations, with claims bound to authenticated trace events. \\
Provenance\-Guard
& Runtime screening of proposed tool actions using evidence for user intent
& Provenance is an advisory representation factor in the primary study;
action blocking is isolated as a separate enforcement intervention. \\
\bottomrule
\end{tabular}
\caption{Claim-level positioning against the closest collisions. Structured
handoffs, state probes, and provenance-aware blocking are prior art; our target
is controlled measurement of semantic state transfer across a role handoff.}
\label{tab:closest-collisions}
\end{table}

\section{Development Findings and Design Adaptation}

We used six counterfactual travel families only to debug the protocol and set
the confirmatory design; these data are excluded from all confirmatory tables.
Across Qwen2.5-14B and Ministral-3-14B (48 scheduled episodes per legacy view),
strict success was 68.8\% for the all-on executable handoff capsule (EHC),
75.0\% for the schema-matched Structured payload, 47.9\% for Free Summary,
91.7\% for Full History, and 93.8\% for the Gold Oracle. The EHC--Structured
difference was $-6.25$ percentage points (family-clustered 95\% CI
$[-22.9,12.5]$). This is a
negative development result: it does not support generic EHC superiority, and
we retain rather than tune it away.

A representation-matched $2\!\times\!2\!\times\!2$ development factorial
(typing, trace-linked provenance, and advisory checks) scheduled 384 cells for
two model families; 381 completed provider/parsing successfully, and all cells remain in
the intent-to-treat denominator. Strict-success main effects were $+2.60$ pp
for typing (95\% CI $[0.52,4.69]$), $-6.77$ pp for provenance
($[-15.63,2.60]$), and $+6.77$ pp for advisory checks
($[3.65,9.38]$). The provenance--checks interaction was $-4.69$ pp
($[-10.42,-0.52]$); provenance also increased mean critical-error count by
0.042 ($[0.010,0.078]$). With only six independent families, these
estimates are diagnostic, not population evidence. They changed the study's
thesis from ``all-on capsules are superior'' to two falsifiable benchmark
questions: whether boundary regression exists, and which representation
mechanisms help or harm under matched information.

Power was likewise treated as a pre-test design input. A fixed-seed simulation
with model repeats nested within family and family-cluster bootstrap inference
estimated, at ICC $=.10$, power of .441 for an 8-pp effect and .633 for a 10-pp
effect at 120 families; at 200 families the corresponding estimates were .691
and .847. We therefore expanded the candidate pool to 200 independently
authored families (40 per domain) before annotation or any candidate model call.
These simulated values are assumptions, not observed test effects, and do not
permit optional stopping.

\section{Confirmatory Results}

The sealed matrix contains all 8,800 scheduled ITT cells: 200 independent
families, two models, two seeds, and eleven conditions. The only two
confirmatory tests sealed before execution use family-cluster percentile-bootstrap
intervals (10,000 draws) and Holm-adjusted two-sided $p$-values. All other
factorial, endpoint, condition, model, and domain estimates below are secondary
or exploratory. Across the matrix, 178 cells (2.02\%; 97 Ministral and 81
Qwen) had non-OK model-output, schema, or parse status; the prespecified ITT
rule retained them with zero success and state credit. Their processing points
were nine source-transfer parses, eight receiver-output parses, 86
receiver-state schema/semantic checks, and 75 receiver action-catalog checks.
The respective Qwen/Ministral splits were 0/9, 1/7, 49/37, and 31/44.
Table~\ref{tab:nonok} shows non-OK rows in every non-oracle condition rather
than a single treatment; Gold Oracle had zero.

\begin{table}[t]
\centering
\small
\begin{tabular}{@{}lrr@{}}
\toprule
Contrast & Effect (pp) & Family 95\% CI \\
\midrule
Structured $-$ Oracle & $-19.50$ & $[-23.63,-15.38]$ \\
Advisory checks & $+3.63$ & $[+1.91,+5.44]$ \\
\bottomrule
\end{tabular}
\caption{The two prespecified confirmatory strict-success tests. Both have
Holm-adjusted $p<.001$ and use ITT rows with family-clustered inference. Rates
appear in the text; effects are percentage points.}
\label{tab:confirmatory-main}
\end{table}

\begin{table}[t]
\centering
\small
\begin{tabular}{@{}lrr@{\qquad}lrr@{}}
\toprule
Condition & Q & M & Condition & Q & M \\
\midrule
F--N--N & 13 & 9 & T--N--N & 4 & 11 \\
F--N--C & 11 & 8 & T--N--C & 4 & 9 \\
F--P--N & 17 & 11 & T--P--N & 1 & 12 \\
F--P--C & 19 & 11 & T--P--C & 5 & 8 \\
Full History & 2 & 8 & Enforced & 5 & 10 \\
\bottomrule
\end{tabular}
\caption{Non-OK ITT cells by condition and model (Qwen Q, Ministral M).
F/T: free-form/typed; N/P: no/trace provenance; N/C: no/computed checks.
Enforced is the typed, provenance, checks-on arm; Gold Oracle had 0/0.}
\label{tab:nonok}
\end{table}

Both prespecified tests rejected their null hypotheses after Holm correction.
Structured transfer reached 71.6\% strict success, compared with 91.1\% under
the Gold Oracle, for a paired effect of $-19.50$ percentage points (95\% CI
$[-23.63,-15.38]$; $p_{\mathrm{Holm}}<.001$). Its oracle-gated HIR incidence
over all scheduled pairs was 21.75\% (95\% CI $[17.88,25.63]$): in these cells,
the oracle succeeded while Structured failed. In the matched representation factorial, advisory
executable checks improved strict success by 3.63 points on average (95\% CI
$[1.91,5.44]$; $p_{\mathrm{Holm}}<.001$), supporting the prespecified
directional hypothesis.

Secondary, unadjusted strict-success estimates were $+1.44$ points for typing
(nominal 95\% CI $[0.06,2.84]$) and $-1.63$ points for trace-linked provenance
($[-2.81,-0.47]$). All two-way interaction intervals crossed zero, as did the
three-way interaction. These mechanism diagnostics are outside the
confirmatory multiplicity family and do not establish general typing benefits
or provenance harms. Secondary endpoints were directionally consistent with a
small diagnostic value for typing: macro state $F_1$ rose by .0098 and mean
critical errors fell by .0766. Checks reduced calls by .075, input tokens by
129, and output tokens by 37 on average, while provenance increased input use
by 891 tokens. These endpoint intervals are likewise unadjusted.

An explicitly post-confirmatory, unadjusted model diagnostic found a checks
effect of $+7.06$ points for Ministral (family-bootstrap 95\% CI
$[3.81,10.50]$) but $+0.19$ for Qwen ($[-0.94,1.38]$); the Qwen-minus-Ministral
difference was $-6.88$ points ($[-10.44,-3.44]$). Thus, the pooled gain did not
replicate in Qwen. These exploratory intervals receive no multiplicity
correction and do not support a universal model or domain claim. Descriptively, Full
History achieved 90.4\%, close to the Oracle's 91.1\%, despite much lower
normalized first-probe state $F_1$; successful action selection need not require
explicit recovery of every probed atom. The all-on advisory and enforced arms
achieved 73.1\% and 74.1\%, respectively, but this difference is not a
confirmatory enforcement test.

\paragraph{Execution and reproducibility.}
The analysis binds dataset seal
\texttt{hb-v3.1-9671bf1ff2d5-20260721} to execution seal
\texttt{hb-v3.4.1-exec-9671bf1ff2d5-20260721}. It combines 4,400 retained
Ministral rows with 4,400 fresh Qwen rows; the invalidated earlier Qwen arm
contributes zero rows. The Qwen ledger records 4,400 written and zero resumed
rows, and the infrastructure audit found no provider infrastructure error.
Bootstrap seed 2027, analysis code hashes, all raw-input hashes, and generated
artifact hashes are recorded in the released provenance manifest.
