\documentclass[letterpaper]{article}
\usepackage[submission]{aaai2027}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\urlstyle{rm}
\def\UrlFont{\rm}
\usepackage{natbib}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning}
\frenchspacing
\pdfinfo{/TemplateVersion (2027.1)}
\setcounter{secnumdepth}{1}

\title{State Is the Interface: Evaluating Handoff Fidelity in Multi-Agent LLM Workflows}
\author{Anonymous Submission}
\affiliations{}

\begin{document}
\maketitle

\begin{abstract}
Multi-agent language-model systems increasingly transfer task ownership between
specialized agents, yet existing evaluations rarely measure which task-critical
state survives the transfer. We introduce HandoffBench, a controlled evaluation
protocol for inter-role handoffs in policy-constrained tool workflows. Each
episode fixes an upstream trace and annotates hidden boundary state: verified
evidence, epistemic unknowns, scoped consent, and policy decisions.
Deterministic receiver-state probes link field fidelity to regression and policy
violations. We compare
full history, free-form summaries, structured payloads, and Executable Handoff
Capsules, which bind typed claims to trace provenance and machine-checkable
preconditions. We seal a pre-execution factorial analysis plan to isolate typing,
provenance, and executable checks under matched evidence and budgets.
Before candidate-model evaluation, isolated agents double-annotated and audited,
replaced exclusions, and sealed a balanced 200-family split. Across 8,800
intent-to-treat runs with two models, two seeds, and eleven conditions,
Structured transfer achieved 71.6\% strict success versus 91.1\% for the Gold
Oracle, a prespecified gap of 19.5 percentage points (family-clustered 95\% CI
$[15.4,23.6]$; Holm-adjusted $p<.001$). Pooled advisory checks improved strict
success by 3.63 points (95\% CI $[1.91,5.44]$; Holm-adjusted $p<.001$).
Exploratory estimates were $+7.06$ points for Ministral and $+0.19$ for Qwen,
revealing model-dependent check utility. Substantial boundary regression thus
remains even with structured state.
\end{abstract}

\section{Introduction}

Handoffs are becoming a standard orchestration primitive: an intake agent may
collect constraints, a policy agent may verify eligibility, and a resolution
agent may execute the final action. The routing decision can be correct while
the workflow still fails. A verified fare can disappear, an unresolved field
can become an assumed value, or approval for one action can be mistaken for
consent to another. These are failures of the interface between agents.

Existing agent benchmarks richly measure tool use, policy compliance, and team
performance \citep{liu2024agentbench,yao2024taubench,lu2025toolsandbox,zhu2025multiagentbench},
while recent coding-agent takeover evaluation measures the effort needed to
resume interrupted work \citep{kc2026handoff}. These works do not, however, expose a gold semantic
state at an inter-role boundary and score which atomic facts, unknowns,
permissions, and preconditions crossed it. Consequently, their end-to-end
scores do not directly quantify regression attributable to a changed boundary
representation under a fixed receiver and environment.

We present HandoffBench, a benchmark and intervention protocol that holds the
upstream trace, target model, tools, and budget fixed while intervening on the
handoff representation. Its central object is a task-critical annotated gold
state whose claims are typed and linked to authenticated user, tool, policy, or
environment events. Core metrics are computed from typed equality, provenance
integrity, simulator transitions, and Boolean success predicates rather than an
LLM judge.

Our contributions are: (1) a controlled benchmark for field-level
handoff fidelity in interactive tool workflows; (2) deterministic state probes
and oracle interventions that identify handoff-induced regression; and (3) a matched
factorial protocol that separates typing, provenance, and advisory executable
checks from action enforcement; and (4) a pre-execution-sealed 8,800-run evaluation
showing a 19.5-point Structured-to-Oracle boundary gap and a 3.63-point average
benefit from advisory checks. Secondary estimates for typing and provenance are
reported separately from the confirmatory multiplicity family.

\input{figures/handoffbench_overview}
\input{sections/method}
\input{sections/benchmark}
\input{sections/evidence}
\input{sections/ethics}

\section{Conclusion}

Reliable multi-agent systems require more than correct routing. Treating the
handoff boundary as a measurable interface exposed a 19.5-point loss from
Structured transfer relative to the Gold Oracle and 21.8\% oracle-gated HIR
incidence over all scheduled pairs. Advisory checks recovered 3.6 points on
average but did not close the boundary gap, and an exploratory split found the
gain only in Ministral, not Qwen. Secondary estimates suggest that serialization
mechanisms need not combine monotonically: typing was mildly beneficial, while
the tested trace-linked provenance implementation incurred a small negative
success estimate and a large token cost. These findings support explicit boundary-state evaluation and
targeted validation, not a blanket claim that richer capsules or enforcement
are universally superior. HandoffBench's contribution is therefore not a
universal capsule recipe, but an outcome-linked, judge-free protocol for making
the handoff interface experimentally measurable.

\bibliography{references}

\end{document}
